\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-03-29 paper/main.tex
Update table, naive predictor on BioSnap

For comparative evaluation, we use the gold standard dataset
introduced by \citet{Yaminishi2008} consisting of 1,923 interactions
between 708 drugs and 1,512 proteins.

@@

	\begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
		\hline
		(c) Approach&\multicolumn{2}{c|}{Original scheme}&\multicolumn{2}{c|}{Protein split}\\
		&Splitting scheme&Macro AUC&Macro AUC&Micro $AUC_p$\\
		\hline
		Naive predictor&DP pairs&$0.85$& --&--\\
		DTINet&DP pairs&$0.91$&$0.74$&$0.67$\\
		DTIGEMS+&DP pairs&$\mathbf{0.93}$& $0.72$& $0.68$ \\
		DTI-CDF&Proteins&$0.85$&$\mathbf{0.85}$&$0.79$\\
		\name&Proteins&$0.84$&$0.84$&$\mathbf{0.84}$\\
		\hline
		\hline
		(d) Approach&\multicolumn{2}{c|}{Original scheme}&\multicolumn{2}{c|}{Protein split}\\
		&Splitting scheme&Macro AUC&Macro AUC&Micro $AUC_p$\\
		\hline
		Naive predictor&DP pairs&$0.79$&-- &--\\
		DeepDTI&Drugs&$0.88$&$0.76$&$0.70$\\
		DeepDTA&DP pairs&$0.88$&$0.77$&$0.69$\\
		DeepConv-DTI&DP pairs&$0.88$&$0.76$&$0.73$\\
		MolTrans&DP pairs&$0.90$&$0.77$&$0.74$\\
		\hline
	\end{tabular}\\

>>>>

For comparative evaluation, we use the gold standard dataset
introduced by \citet{Yaminishi2008} consisting of 1,923 interactions
between 708 drugs and 1,512 proteins, and BioSnap dataset \cite{BioSnap2018}, which consists of 5,017 drug nodes, 2,324 gene nodes and 15,138 edges.

@@

	\begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
		\hline
		&&\multicolumn{3}{c|}{(c) Yamanishi results}&\multicolumn{3}{c|}{(d) BioSnap results}\\
		Approach&Original&Original scheme&\multicolumn{2}{c|}{Protein split}&Original scheme&\multicolumn{2}{c|}{Protein split}\\

		&Splitting scheme&Macro AUC&Macro AUC&Micro $AUC_p$&Macro AUC&Macro AUC&Micro $AUC_p$\\
		\hline
		Naive predictor&DP pairs&$0.85$& --&--&$0.79$&-- &--\\
		DTINet&DP pairs&$0.91$&$0.74$&$0.67$ & --&--&--\\
		DTIGEMS+&DP pairs&$\mathbf{0.93}$& $0.72$& $0.68$ & --&--&--\\
		DTI-CDF&Proteins&$0.85$&$\mathbf{0.85}$&$0.79$& --&--&--\\
		\hline
		DeepDTI&Drugs& --&--&--&$0.88$&$0.76$&$0.70$\\
		DeepDTA&DP pairs& --&--&--&$0.88$&$0.77$&$0.69$\\
		DeepConv-DTI&DP pairs& --&--&--&$0.88$&$0.76$&$0.73$\\
		MolTrans&DP pairs& --&--&--&$0.90$&$0.77$&$0.74$\\
		\name&Proteins&$0.84$&$0.84$&$\mathbf{0.84}$& & & \\
		\hline
	\end{tabular}\medskip
